### 2016-01-16 paper.tex
Remove duplicate word
Clean up strut covers description

For investigating the effects of support strut drag losses, a set of cylindrical
strut covers was designed to slip over the blades. Endcaps were also fabricated
to allow the high drag strut cover configuration to be operated without blades.
A drawing of the strut covers is shown in Fig.~\ref{fig:covers}.

@@

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed precise control
of the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted, mounted at a fixed distance from the
servo motor, provides a redundant measurement. Turbine shaft angle was measured
using the servo drive's emulated encoder output, set to $10^5$ counts per
turbine shaft revolution. Carriage speed, and therefore inflow velocity was
measured using a linear encoder with 10 $\mu$m resolution. All of these
performance-related quantities were sampled at 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed turbine
angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

>>>>

For investigating the effects of support strut drag losses, a set of cylindrical
covers were designed to slip over the struts, which provided a significant
increase in strut drag. Endcaps were also fabricated to allow the high drag
strut cover configuration to be operated without blades. A drawing of the strut
covers is shown in Fig.~\ref{fig:covers}.

@@

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed precise control
of the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted at a fixed distance from the servo motor,
provides a redundant measurement. Turbine shaft angle was measured using the
servo drive's emulated encoder output, set to $10^5$ counts per turbine shaft
revolution. Carriage speed, and therefore inflow velocity was measured using a
linear encoder with 10 $\mu$m resolution. All of these performance-related
quantities were sampled at 2 kHz, while the tow tank's motion controller
provided redundant measurements of the carriage speed turbine angular velocity
sampled at 1 kHz. Turbine wake measurements at 1 meter downstream were measured
with a Nortek Vectrino+ acoustic Doppler velocimeter, sampling at 200 Hz. A
photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
